EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-10 paper/paper.tex
added a test case

\maketitle
\begin{abstract}
Code clones are common in medium to large scale software projects. Oftentimes, unnecessary clones cause troubles to code base maintenance and code reusability. 
Over past decades, many techniques and approaches have been proposed to detect code clones. However, how to refactor clones is still a challenging topic to software
engineers. Even text-wise identical code clones can be semantically different when they are referring variables and calling functions outside. And the problem is more 
complex when scopes and dependencies are considered. Furthermore, not all clones can be refactored as they may be part of tests or needed to maintain dependencies across multiple
libraries. As a result, we need adaptive clone refactoring tools that can locate unnecessary clones and alert possible implications in the procedure to help
software engineers be more efficient and make less mistakes in the refactoring process.

In this paper, we introduce EasyMerge, a new tool to refactor code clones.
\end{abstract}

@@

\keywords{Software Engineering, Clone Detection, Code Refactoring, Recommendation System} % NOT required for Proceedings

>>>>

\maketitle
\begin{abstract}
Code clones are common in medium to large scale software projects. Oftentimes, unnecessary clones cause troubles to code base maintenance and code reusability. 
Over past decades, many techniques and approaches have been proposed to detect code clones. However, how to refactor clones is still a very challenging topic to software
engineers. Even text-wise identical code clones can be semantically different when they are referring variables and calling functions outside. And the problem is more 
complex when scopes and dependencies are considered. Furthermore, not all clones can be refactored as they may be part of tests or needed to maintain dependencies across multiple
libraries. As a result, we need adaptive clone refactoring tools that can locate unnecessary clones and alert possible implications in the procedure to help
software engineers be more efficient and make less mistakes in the refactoring process.

In this paper, we introduce EasyMerge, a new tool to refactor code clones. EasyMerge is built on top of AST-based clone detection algorithm
\end{abstract}

@@

\keywords{Software Engineering, Clone Detection, Code Refactoring, Recommendation System, Python} % NOT required for Proceedings
